Many-core applications to online track reconstruction in HEP experiments

### 2013-10-03 papers/2013/CHEP/paper.tex
ref and title fixes

\documentclass[letterpaper]{jpconf}
\usepackage{graphicx}
\usepackage{iopams}
\usepackage[pdftex,
      colorlinks=true,
      urlcolor=blue,       % \href{...}{...} external (URL)
      filecolor=green,     % \href{...} local file
      linkcolor=red,       % \ref{...} and \pageref{...}
      pdftitle={Papers by Peter Wittich},
      pdfauthor={Peter Wittich},
      pdfsubject={Just a test},
      pdfkeywords={test testing testable},
      pagebackref,
      pdfpagemode=UseNone,
       bookmarksopen=true]{hyperref}

\begin{document}
% paper title
\title{Applications of GPUs to Online Track Reconstruction in HEP Experiments}
% Author list
\author{S.~Amerio$^1$, 
  D.~Bastieri$^1$, 
  M.~Corvo$^1$, 
  A.~Gianelle$^1$, 
  D.~Lucchesi$^1$,
  T.~Liu$^2$, 
  R.~Rivera$^2$, 
  W.~Ketchum$^3$,
  S.~Poprocki$^4$, P.~Wittich$^4$,
  A.~Lonardo$^5$, and P.~Vicini$^5$
}
\address{$^1$ INFN and University of Padova, Italy}
\address{$^2$ Fermi National Accelerator Laboratory, Illinois, USA}
\address{$^3$ Los Alamos National Laboratory, New Mexico, USA}
\address{$^4$ Cornell University, New York, USA}
\address{$^5$ INFN Roma, Italy}

@@

%% gives unnumbered ack in CHEP style
\ack
The authors would like to thank the Fermilab staff and the FTK group at the 
University of Chicago for their support. This work was supported by the
U.S. Department of Energy and National Science Foundation and the Italian
Istituto Nazionale di Fisica Nucleare.

%% CHEP2013 recommended style
\bibliographystyle{iopart-num}

>>>>

\documentclass[letterpaper]{jpconf}
\usepackage{graphicx}
\usepackage{iopams}
\usepackage[pdftex,
      colorlinks=true,
      urlcolor=blue,       % \href{...}{...} external (URL)
      filecolor=green,     % \href{...} local file
      linkcolor=red,       % \ref{...} and \pageref{...}
      pagebackref,
      pdfpagemode=UseNone,
      bookmarksopen=true]{hyperref}

\begin{document}
% paper title
\title{Many-core applications to online track reconstruction in HEP experiments}
% Author list
\author{S.~Amerio$^1$, 
  D.~Bastieri$^1$, 
  M.~Corvo$^1$, 
  A.~Gianelle$^1$, 
  W.~Ketchum$^2$,
  T.~Liu$^3$, 
  A.~Lonardo$^4$, 
  D.~Lucchesi$^1$,
  S.~Poprocki$^5$, 
  R.~Rivera$^2$, 
  P.~Vicini$^4$
  and 
  P.~Wittich$^5$,
}
\address{$^1$ INFN and University of Padova, Italy}
\address{$^2$ Los Alamos National Laboratory, New Mexico, USA}
\address{$^3$ Fermi National Accelerator Laboratory, Illinois, USA}
\address{$^4$ INFN Roma, Italy}
\address{$^5$ Cornell University, New York, USA}

@@

%% gives unnumbered ack in CHEP style
\ack
The authors would like to thank the Fermilab staff and the FTK group at the 
University of Chicago for their support. This work was supported by the
U.S. Department of Energy, the U.S. National Science Foundation and the Italian
Istituto Nazionale di Fisica Nucleare.

%% CHEP2013 recommended style for bibliography
\bibliographystyle{iopart-num}
